An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-04 EconGrowth-R-Functions.Rnw
Now creating graphs for ZA in the presentation. But, they are too large.

<<setup_parent, echo=FALSE, message=FALSE, eval=TRUE>>=
require(knitr)
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
opts_chunk$set(
  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
  tidy=FALSE,
  comment=NA,
  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (cache=TRUE).
  cache=FALSE,
  warning=TRUE,  #Tells whether to show warnings in the output.
  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
)

@@

cdModel("US")

@@

###############################
# Does a grid search over values of gamma for a CD production function
##
cdGrid <- function(countryAbbrev, energyType, gammaGrid){
  gamma <- gammaGrid
  models <- lapply(gamma, cobbDouglasModel, energyType=energyType, countryAbbrev=countryAbbrev)
  return(models)
}

gammaGrid <- seq(0.0, 0.95, by=0.05)
# print("US")
# models <- cdGrid("US", "Q", gammaGrid)
# SSE <- lapply(models, function(model) summary(model)$sigma)
# data <- cbind(gammaGrid, SSE)
# plot(gammaGrid, SSE)
# print(coef(models[[2]]))
# 
print("ZA")
models <- cdGrid("ZA", "Q", gammaGrid)
SSE <- lapply(models, function(model) summary(model)$sigma)
lambda <- lapply(models, function(model) coef(model)["lambda"])
alpha <- lapply(models, function(model) coef(model)["alpha"])
data <- cbind(lambda, alpha, gammaGrid, SSE)
plot(gammaGrid, SSE)
plot(gammaGrid, lambda)
plot(gammaGrid, alpha)

# Some code to debug the Cobb-Douglas models. Randy Pruim is helping on this.

# print("cobbDouglasModel(US, Q) works fine:")
# us <- cobbDouglasModel("US", "Q")
# print(summary(us))
# print(confint(us))
# 
# print("cobbDouglasModel(ZA) works fine")
# za <- cobbDouglasModel("ZA")
# print(summary(za))
# print(confint(za))
# 
# print("cobbDouglasModel(ZA, Q) stops before convergence achieved,")
# print("and confint gives NA values:")
# za <- cobbDouglasModel("ZA", "Q")
# print(summary(za))
# print(confint(za))
# 
# print("cobbDouglasModel(UK, Q) also stops before convergence achieved,")
# print("but confint does not produce NA values:")
# uk <- cobbDouglasModel("UK", "Q")
# print(summary(uk))
# print(confint(uk))

# save(us, za, uk, file="HeunModels-US-ZA-UK.Rdata")

>>>>

<<setup_parent, echo=FALSE, message=FALSE, eval=TRUE>>=
require(knitr)
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
opts_chunk$set(
  # ********************************************************************************************************
  eval=TRUE,
  # ********************************************************************************************************
  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
  tidy=FALSE,
  comment=NA,
  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (cache=TRUE).
  cache=FALSE,
  warning=TRUE,  #Tells whether to show warnings in the output.
  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
)

@@

@@

###############################
# Does a grid search over values of gamma for a CD production function
##
cdeGridData <- function(countryAbbrev, energyType, gammaGrid){
  gamma <- gammaGrid
  models <- lapply(gamma, cobbDouglasModel, energyType=energyType, countryAbbrev=countryAbbrev)
  return(models)
}

#############################
# This function creates a series of graphs for Cobb-Douglas with energy functions
# showing various parameters as a function of gamma.
##
cdeGridGraphs <- function(countryAbbrev, energyType){
  gammaGrid <- seq(0.0, 0.95, by=0.05)
  #print(paste(countryAbbrev, energyType))
  models <- cdeGridData(countryAbbrev, energyType, gammaGrid)
  SSE <- lapply(models, function(model) summary(model)$sigma)
  lambda <- lapply(models, function(model) coef(model)["lambda"])
  alpha <- lapply(models, function(model) coef(model)["alpha"])
  data <- cbind(lambda, alpha, gammaGrid, SSE)
  plot(gammaGrid, SSE)
  plot(gammaGrid, lambda)
  plot(gammaGrid, alpha)
}

### 2013-03-04 EconGrowth.Rnw
Now creating graphs for ZA in the presentation. But, they are too large.

<<setup_child, child='EconGrowth-R-Functions.Rnw', echo=FALSE, message=FALSE, eval=TRUE>>=
# Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
opts_chunk$set(
  # ********************************************************************************************************
  eval=TRUE,
  # ********************************************************************************************************
  warning=TRUE,  #Tells whether to show warnings in the output.
  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
) 
@

@@

>>>>

<<setup_child, child='EconGrowth-R-Functions.Rnw', echo=FALSE, message=FALSE, eval=TRUE>>=
# Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
@

@@

The Cobb-Douglas with energy parameter estimation process is problematic. The following graphs show that the minimum of the squared-errors curve occurs at the point where $\beta$ --> 0.0.

<<CDeGammaGraphsZA, eval=TRUE>>=
  cdeGridGraphs("ZA", "Q")
@

### 2013-03-04 EconGrowthSeminar.Rnw
Allowing .pdf graphics in the repository now. Also, clearing a lot of old files with .aux and .spl extensions.
Now creating graphs for ZA in the presentation. But, they are too large.

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

% Since this a solution template for a generic talk, very little can
% be said about how it should be structured. However, the talk length
% of between 15min and 45min and the theme suggest that you stick to
% the following rules:

% - Exactly two or three sections (other than the summary).
% - At *most* three subsections per section.
% - Talk about 30s to 2min per frame. So there should be between about
%   15 and 30 frames, all told.

@@

\begin{frame}{Economic (Growth) Modeling} %----------------------------
  \begin{center}
    \includegraphics[height=2.5cm]{figure/Figure_Growth_Models.pdf}
  \end{center}
  \begin{itemize}
  \item
    Goal: predict economic output over time
  \item
    Economic output is a function of ``factors of production''
  \item
    Output defined as GDP ($Y$)
  \item
    All inputs and outputs normalized to initial year (0)
  \end{itemize}
\end{frame}

@@

\begin{frame}{Example Cobb-Douglas Fit} %----------------------------
  Heun complete
\end{frame}

@@

\end{document}

>>>>

\begin{document} %**************************************************

\begin{frame} %----------------------------
  \titlepage
\end{frame}

\begin{frame}{Outline} %----------------------------
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

<<setup_child, child='EconGrowth-R-Functions.Rnw', echo=FALSE, message=FALSE, eval=TRUE>>=
# Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
@

@@

\begin{frame}{Economic (Growth) Modeling} %----------------------------
  \begin{center}
    \includegraphics[height=2.5cm]{figure_other/Figure_Growth_Models.pdf}
  \end{center}
  \begin{itemize}
  \item
    Goal: predict economic output over time
  \item
    Economic output is a function of ``factors of production''
  \item
    Output defined as GDP ($Y$)
  \item
    All inputs and outputs normalized to initial year (0)
  \end{itemize}
\end{frame}

@@

\begin{frame}{Example Cobb-Douglas Fit} %----------------------------
<<CDeGammaGraphsZA, eval=TRUE>>=
  cdeGridGraphs("ZA", "Q")
@
\end{frame}

@@

\end{document} %**************************************************
